%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
%---------------------------------------------------------
%---------------------------------------------------------
\cventry
    {Software Engineer | DevOps | IAM Specialist} % Job title
    {Kaluza} % Organisation
    {London} % Location
    {Jun 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led Identity Provider (Keycloak) integration, enhancing security and streamlining infrastructure for an estimated \$3,000/month in cost savings.}
        \item {Developed a robust load testing framework ensuring 99.99\% uptime.}
        \item {Developed Go-based data scraper to mitigate a major cyber incident, securing >800 accounts, preventing >100k user data exposures.}
        % \item {Orchestrated IAM service migration, simplifying legacy systems to a new cloud platform with zero downtime or critical incidents.}
        \item {Managed Out-Of-Hours (OOH) rota, improving operational readiness, streamlining incident response, and ensuring 24/7 service coverage.}
        \item {Delivered critical data migration support, rapidly providing complex PDF rendering solutions.}
        \item {Optimised CI/CD efficiency, building validation tools, reducing average build times by >80\% (11 to 2 minutes), enhancing developer experience.}
        \item {Enhanced operational security, patching >200 repositories to simplify vulnerability resolution and strengthening critical service infrastructure.}
        \item {Spearheaded automation initiatives, migrating >40 repos to GitHub Actions (\$50,000+ annual savings), reducing manual support by 15-20\%.}
        \item {Developed Authorisation Decision Point (Adept) in Scala, a core HTTP service simplifying real-time access queries and enabling granular control.}
        % \item {Led overhaul of configuration management, establishing a unified platform that reduced code review context switching by 20\%.}
        % \item {Evolved Developer Portal, driving Docusaurus/Next.js adoption and Cypress E2E/Accessibility integration for WCAG 2.1 AA compliance.}
        % \item {Automated documentation generation with an internal tool for GraphQL schemas, drastically reducing manual work, saving ~100+ hours annually.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Engineer} % Job title
    {OVO Energy} % Organisation
    {London, United Kingdom} % Location
    {Jun 2020 - Jun 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered customer-facing features with React, TypeScript, and Styled Components for the Energy Insights team.}
        \item {Delivered personalised recommendations that empowered customers to reduce energy consumption.}
        \item {Built numerous reusable React components for both web and mobile (React Native), streamlining cross-platform development.}
        \item {Developed organizational CircleCI orbs for internal teams, enhancing CI/CD standardization and reusability.}
        % \item {Engineered and deployed a standalone FastAPI application within three months, containerised for serverless AWS Fargate.}
        % \item {Contributed to the software development lifecycle, utilising GraphQL, Node.js, and backend systems in Scala.}
        \item {Managed and optimised cloud infrastructure on AWS and GCP, ensuring robust CI/CD with CircleCI for automated deployments.}
        % \item {Collaborated with product teams, delivering high-quality code and participating in code reviews.}
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}
