\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,top=1.1in,bottom=1in,left=0.75in,right=0.75in]{geometry}
\usepackage{tikz}
\usepackage{calc}
\usetikzlibrary{calc}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{xcolor}
\definecolor{MyGray1}{RGB}{128,128,128}

\newcommand{\ulfrule}{\xleaders\hbox{\underline{ }}\hfill\kern0pt}

\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\linespread{2}

\usepackage{lastpage}
\usepackage{sectsty}
\sectionfont{\fontsize{16}{18}\selectfont}

\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
\fancyhead[C]{%
\begin{tikzpicture}[overlay, remember picture]%
    \fill[black] ($(current page.north west)+(2in,-0.45in)$) rectangle ($(current page.north east)+(-2in,-0.8in)$);
    \draw[black,thick] ($(current page.north west)+(0.5in,-1.3in)$) -- ($(current page.north east)+(-0.5in,-1.3in)$) -- ($(current page.south east)+(-0.5in,1.1in)$) -- ($(current page.south west)+(0.5in,1.1in)$) -- ($(current page.north west)+(0.5in,-1.3in)$);
    \node[text=white] at ($(current page.north)+(0in,-0.67in)$) {\fontsize{13}{14}\selectfont\textbf{RESTRICTED  (when complete)}};
    \node[anchor=north east, text=black] at ($(current page.north east)+(-0.35in,-0.35in)$) {\fontsize{10}{12}\selectfont\bf MG 11 (CONT)};
    \node[anchor=north east, text=black] at ($(current page.north east)+(-0.5in,-0.8in)$) {\fontsize{10}{12}\selectfont\bf Page No.  \thepage\ of \pageref{LastPage}};
    \node[anchor=north west, text=black] at ($(current page.north west)+(0.5in,-1.05in)$) {\fontsize{11}{12}\selectfont\bf Continuation of Statement of  Alessandro BUONERBA};
\end{tikzpicture}
}

\fancyfoot[C]{%
\begin{tikzpicture}[overlay, remember picture]%
    \fill[black] ($(current page.south west)+(2in,0.3in)$) rectangle ($(current page.south east)+(-2in,0.65in)$);
    \node[text=white] at ($(current page.south)+(0in,0.43in)$) {\fontsize{13}{14}\selectfont\textbf{RESTRICTED  (when complete)}};
    \node[anchor=south west, text=black] at ($(current page.south west)+(0.8in,1.2in)$) {\fontsize{10}{12}\selectfont Signature: \quad \fontsize{8}{10}\selectfont Alessandro Buonerba};
    \draw[black,thick,dotted] ($(current page.south west)+(1.55in,1.22in)$) -- ($(current page.south west)+(3.87in,1.22in)$);
    \node[anchor=south west, text=black] at ($(current page.south west)+(3.95in,1.2in)$) {\fontsize{10}{12}\selectfont Signature witnessed by: \quad \fontsize{6}{8}\selectfont Not Required for Professional Witnesses};
    \draw[black,thick,dotted] ($(current page.south east)+(-2.7in,1.22in)$) -- ($(current page.south east)+(-0.67in,1.22in)$);
    \node[anchor=south east, text=MyGray1] at ($(current page.south east)+(-0.77in,0.43in)$) {\fontsize{11}{12}\selectfont CW/1/3};
\end{tikzpicture}
}






\begin{document}
%------------------------------------------
%   First Page
%------------------------------------------
\thispagestyle{empty}

\begin{tikzpicture}[overlay, remember picture]%
    \fill[black] ($(current page.north west)+(2in,-0.3in)$) rectangle ($(current page.north east)+(-2in,-0.65in)$);
    \draw[black,thick] ($(current page.north west)+(0.53in,-0.82in)$) -- ($(current page.north east)+(-0.53in,-0.82in)$) -- ($(current page.south east)+(-0.53in,1.1in)$) -- ($(current page.south west)+(0.53in,1.1in)$) -- ($(current page.north west)+(0.53in,-0.815in)$);
    \node[text=white] at ($(current page.north)+(0in,-0.52in)$) {\fontsize{13}{14}\selectfont\textbf{RESTRICTED  (when complete)}};
    \node[anchor=north east, text=black] at ($(current page.north east)+(-0.43in,-0.31in)$) {\fontsize{8}{10}\selectfont \textbf{Form MG 11}};
    %
    \draw[black,thick] ($(current page.north west)+(0.53in,-3.2in)$) -- ($(current page.north east)+(-0.53in,-3.2in)$);
    \draw[black,thick] ($(current page.north west)+(0.53in,-4.7in)$) -- ($(current page.north east)+(-0.53in,-4.7in)$);
\end{tikzpicture}

\vspace{-3.5em}

\begin{center}
    \fontsize{16}{18}\selectfont \textbf{WITNESS STATEMENT}

    \fontsize{10}{12}\selectfont CJ Act 1967, s.9; MC Act 1980, ss.5A(3) (a) and 5B; Criminal Procedure Rules 2020, Rule 16.2
\end{center}

\hfill \fontsize{10}{12}\selectfont \begin{tabular}{r|@{}p{0.4in}|@{}p{0.4in}|@{}p{0.8in}|@{}p{0.4in}|} \cline{2-5}
URN & & & & \\ \cline{2-5}
\end{tabular}

\medskip

Statement of: \underline{\makebox[0.85\textwidth][l]{Alessandro Buonerba BSc(Hons) Computer Science (Cyber Security)}}

Age if under 18: \underline{\makebox[0.2\textwidth][l]{Over 18}}	{\fontsize{8}{10}\selectfont(if over 18 insert ‘over 18’)} \quad	Occupation:	\underline{\makebox[0.3\textwidth][l]{Digital Forensics Specialist}}

\bigskip

This statement (consisting of 7 pages each signed by me) is true to the best of my knowledge and belief and I make it knowing that, if it is tendered in evidence, I shall be liable to prosecution if I have wilfully stated in it, anything which I know to be false, or do not believe to be true.

Signature: \underline{\makebox[0.5\textwidth][l]{\textbf{Alessandro Buonerba}}} \qquad Date: \underline{\makebox[0.3\textwidth][l]{29/10/2021}}

\bigskip\medskip

Tick if witness evidence is visually recorded \quad \begin{tabular}{|@{}p{0.25in}|} \hline
\\ \hline
\end{tabular} \quad \textit{(supply witness details on rear)}


\fontsize{11}{12}\selectfont

\section*{Qualifications and Experience}
\begin{enumerate}
    \item I am employed as a Digital Forensics Specialist at Greenwich Police High Tech Forensics Unit. I have worked in the field of Computer Forensics since 2018. I have Bachelor of Science degree in Computer Science (Cyber Security) from the University of Greenwich. I have undertaken specialist training in Digital Forensics as part of my degree from the University of Greenwich.
    \item I have performed various examinations for both law enforcement and commercial organisations.  I have previously given evidence in Court as an expert witness in relation to forensic computing cases.
\end{enumerate}

\section*{Background}
\begin{enumerate}[resume]
    \item This witness statement refers to actions I have undertaken during the examination of a forensic image supplied to me at the Greenwich Police High Tech Forensics Unit in the case referred to as Operation Blue 3.
\end{enumerate}


%------------------------------------------
%   Second Page
%------------------------------------------
\newpage
\newgeometry{top=1.5in,bottom=1.7in,left=0.75in,right=0.75in}
\fontsize{11}{12}\selectfont

\begin{enumerate}[resume]
    \item This statement should be read in conjunction with that of my colleague, Mr. A. Aaron Adamson who is the imaging technician in this case.
    \item The exhibit to which my examination refers is as follows: A forensic image file called ‘Operation Blue 3 - 2021.E01’, relating to exhibit ABL/1, a USB drive.
    \item Following instructions from the investigating officer I have conducted an examination of the of the image file in order assist the investigation into alleged drugs offences.
    \item My examination was conducted using sound forensic methodology, tools and practices. I have followed the ‘Good Practice Guide for Digital Evidence’ produced by the Association of Chief Police Officers (ACPO).
    \item During my examination I recorded my actions and observations in my original notes. These notes provide more detailed technical aspects of the forensic image of the exhibit and the processes and tools that I used. They can be produced if required.
\end{enumerate}

\section*{Summary of Findings}
\begin{enumerate}[resume]
    \item 1 (one) artefact that present password hiding techniques
    \item 2 (two) artefacts present on device that show conversations between two entities
    \item 5 (five) artefacts are present that link towards a website
    \item 1 (one) artefact of a CV
    \item 25 (twenty-five) artefacts related to drugs
    \item 4 (four) artefacts of child pornography
    \item 5 (five) artefacts of pornography
\end{enumerate}

\section*{Detailed Findings for Exhibit ABL/1}
\begin{enumerate}[resume]
    \item The file ‘Operation Blue 3 - 2021.E01’ is the forensic image of the USB drive of exhibit ABL/1. For the remainder of the statement, I will refer to my examination as being on exhibit ABL/1.
    \item ABL/1 contains the NTFS file system and is 2045MB in size. My examination shows that the last recorded use of the computer was on 18/10/2021 at 18:11:09.
    \item The currently installed operating system is Windows 10 Enterprise Evaluation with a recorded installation/update date of 19th of March at 12:59:35. The registered owner is recorded as Piet and there is a single (1) user account present named IEUser which has a password set for it. My examination shows that the last recorded use of the computer was on 18/10/2021 at 18:11:09.
\end{enumerate}

%\section*{Feel free to add or remove any of the artefact sections, or reorder them based upon your perception of their importance to the reader.}

\section*{Documents and Notable Files}
\begin{enumerate}[resume]
    \item I searched ABL/1 using the Autopsy version 4.19.1.
    \item One of the documents found is “Note to self.txt” created on 2021-10-19 12:30:30 BST and located in the “/Work/” folder. This file contains the following sentence: “better yet, make a website where we can just mail this stuff to people without the stupid driving around”.
    \item 4 (four) more documents are found in the “Work/Home sweet home\_files/” folder. The files are named “Home sweet home.html”, “How much do drugs cost\_ – DrugWise.html” and “How much do drugs cost\_ – DrugWise.html”, which are artifacts 4, 5 and 6 in the order presented. These files are web pages that are related to inform and sell drugs to the viewer of the page. The meta-data of all the files are also included in the evidential extraction.
    \item A CV in a format of a Rich Text File has been found in the Work directory. The CV has some information about “Simon Piet van der Valk” and it emphasise the fact that is still doing University and that he has web design skills. The CV seems to be only a draft as it contains unfinished sentences. I have included the notable files on the evidential extraction, AB/1.
\end{enumerate}

\section*{Pictures and Video}
\begin{enumerate}[resume]
    \item 25 (twenty-five) artefacts (from 11 to 36) related to drugs have been found in the folder “/Work”. All images listed here depict pictures of drugs which were found on the device.
    \item 4 (four) artefacts representing child pornography have also been found in a folder hidden inside another folder named “delete.jpg”. The name of the folder containing the material is “nawty kitty” and has been create on 2021-10-19 at 12:30:30 BST.
    \item 5 (five) more images of pornography have been found in the “Work/Fun times/Fun times/” folder where they have been created on 2021-10-19 at 12:30:30 BST. I have included the notable pictures on the evidential extraction, AB/1.
\end{enumerate}

\section*{Chat Artefacts}
\begin{enumerate}[resume]
    \item 2 (two) documents containing chat messages sent to “JamesP” and “Ellie” have been found. The files are named after the name of the recipient such as “JamesP.txt” and “Ellie.txt” and are located in the “backups/greSTYLE chat/Logs/” folder. The message exchanges made in the JamesP files states that the subject has recently bought a new laptop. Additionally, he addresses himself as the “dutchman” and to Miss Ellie as “Piet” and shows his preoccupation about the cops to JamesP. I have included the notable Internet history on the evidential extraction, AB/1.
\end{enumerate}

\section*{Registry Artifacts}
\begin{enumerate}[resume]
    \item Two (2) Registry Files were found on this device located “/img\_Operation Blue 3 - 2021.E01/vol\_ vol2/backups/Registry/”. The name of the files is SAM \& SOFTWARE. An application called Windows Registry Recovery was used to examine and open these files. The user would need to use specific tools to view the files. Within “SAM” the IEUser is set with the name “Piet” and the last login can be seen as “18/10/2021 18:11:09”. The user was online for 6 hours and then changed the password set at “19/10/2021 02:01:47” Meta-data for the registry files has been added to the evidential extraction.
\end{enumerate}

\section*{Conclusions}
\begin{enumerate}[resume]
    \item As stated in the section 20, there is a note that shows the intention of the creation of a website to sell unknown items. This combined to the evidence of a Drupal website and related images of the items and drugs sold would be a premeditated intention of marketing the illegal substances over the internet to customers around the world.
    \item In the section 21, there were files related to a Drupal website containing all drug pictures that have been disclosed previously. Specifically, there was a webpage explaining the cost of the drugs. This could suggest that the owner of the USB wanted to purchase or sell drugs at internet standard price.
    \item In section 22, the CV displays information’s of the suspect name, being Simon Pier Van Der Valk, this would suggest that he is the owner of the document. The last sentence is: “Blah blah... there is a reason I don’t do real jobs blah”, which could hide a subliminal message.
    \item In section 23, It seems as the pictures are used as a thumbnail for a website that is used as a marketplace where users can buy drugs and get it delivered at home. The name of the files is also the name of the drugs that are shown in the pictures. Some images have also been given a different extension (Artifact 33/34/35/36, where the extension has been changed to .php) in hope to hide the content.
    \item In section 24 and 25, illegal material such as child-pornography has been found in the USB device. This could link to different crimes not related to drugs.
    \item The fact that only a laptop bag has been found in the apartment of the suspect is connected to the section 26, where messages to JamesP states that he would bring his new laptop over to work on something. This suggest that the last statement on the status of his computer made on the scene could not be true, as the evidence suggests otherwise.
    \item In section 27 the registry files show that a user named “Piet” logged on to a device containing Windows 10. This time shows that it is in the timeframe of when Mr Piet Van Der Valk claims to not of had access to a computer. The name of the user links to the same name of the suspect who is in question. This name also appears again in section 26.
    \item Many files have the same date of creation, meaning that they have been transferred from a device to this USB in batch and are not the main source of truth.
\end{enumerate}

\section*{Exhibit Production}
\begin{enumerate}[resume]
    \item As a result of my analysis I produce the following exhibit:

    \begin{tabular}{lll}
    \textbf{Exhibit} & \textbf{Bag Seal} & \textbf{Description of Exhibit} \\
    \textbf{AB/1} & Unsealed & Evidential Extraction Document \\
    \end{tabular}

    \item I have attached to this statement the evidential extraction, exhibit your AB/1.
\end{enumerate}

\section*{Disclosure}
\begin{enumerate}[resume]
    \item I confirm that I have complied with my duties to record, retain and reveal material in accordance with the Criminal Procedure and Investigations Act 1996, as amended.
    \item In the event my opinion changes on any material issue, I will inform the investigating officer as soon as reasonably practicable and give reasons.
\end{enumerate}

\section*{Duty to the Court}
\begin{enumerate}[resume]
    \item I declare that I understand that my duty, including providing written reports and giving evidence, is to assist the court and that this duty overrides any obligation to the party who has engaged me. I can confirm that I believe that I have complied with my duty.
    \item I confirm that, to the best of my knowledge and belief, I have acted in accordance with the Code of Conduct published by the Forensic Science Regulator (Issue 4) in all aspects that relate to my personal conduct. Alessandro Buonerba
\end{enumerate}


\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
\hspace{1in} \begin{tikzpicture}[x=1pt,y=0.75pt,yscale=-1,xscale=1]
\draw [color={rgb, 255:red, 248; green, 231; blue, 28 }  ,draw opacity=1 ,->][line width=3]    (0,0) .. controls (700,30) and (0,60) .. (10,100) .. controls (650,140) and (0,160) .. (10,220) .. controls (39.8,246.6) and (239.16,268.69) .. (276.52,274.26) ;
\end{tikzpicture}
\end{document}
